Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application

### 2023-10-10 Article.tex
Add paragraph of comments for fig 16

\begin{figure}[H]
\centering
\includegraphics[width=0.90\columnwidth]{Figures/ExpNum}
\caption{Experimental and numerical $X_{drx}$ values for $T_0=1050\celsius$, strain rate $\mdot{\varepsilon}=0.001~\ps$ and $45\%$ reduction ($\varepsilon=0.55$).}
\label{fig:expNumDRX2}
\end{figure}

>>>>

\textcolor{purple}{Figure \ref{fig:expNumDRX2} shows a comparison of the numerical results for a strain rate $\mdot\varepsilon=0.001~\ps$, an initial temperature $T=1050~\celsius$ and a reduction of $45\%$ (\ie $\varepsilon=0.55$) and its comparison with the microstructure obtained experimentally for the same conditions after an interrupted test with the same reduction level. It can be seen later that there is a correspondence between the fully recrystallized area in the center of the sample (the red zone in the numerical simulation) and the corresponding zone where the microstructure has changed in the center of the sample, promoting a labrys (a double-edged) axe shape. As can be clearly seen on the micrograph, recrystallization is not complete in the areas of contact with the upper and lower anvils, where the numerical value of $X_{drx}$ is less than $5\%$ and the microstructure enhances very large grains. We can also see on the microstructure that recrystallization is not complete along the periphery of the cylinder, where the numerical value of $X_{drx}$ is in the range of $75\%$ to $90\%$.}
\begin{figure}[H]
\centering
\includegraphics[width=0.90\columnwidth]{Figures/ExpNum}
\caption{\textcolor{purple}{Comparison of the micrography and numerical $X_{drx}$ values for $T_0=1050\celsius$, strain rate $\mdot{\varepsilon}=0.001~\ps$ and $45\%$ reduction ($\varepsilon=0.55$).}}
\label{fig:expNumDRX2}
\end{figure}
